God in Coq: \\ Modal Logic in Coq \\ and Scott's Version of G\"{o}del's Proof of God's Existence \\ {\small (\emph{Rough Diamond Proof Pearl})}

### 2014-01-23 Papers/ITP/GodProof-ITP.tex
Update paper

\begin{verbatim}
Definition mnot (p: o)(w: i) := ~ (p w).
Notation "m~  p" := (mnot p) (at level 74, right associativity).

@@

\noindent
Validity of a modal proposition is validity of the grounded proposition on any world.

\noindent
Although

@@

@@

@@

>>>>

\begin{verbatim}
Definition mequal (x y: u) := fun w: i => x = y.
Notation "x m= y" := (mequal x y) (at level 99, right associativity).

Definition mnot (p: o)(w: i) := ~ (p w).
Notation "m~  p" := (mnot p) (at level 74, right associativity).

@@

\noindent
Although the embedding via the possible world semantics is necessary, it should be as transparent as possible to the user. Fortunately, basic Coq tactics such \texttt{intro}, \texttt{apply} and \texttt{split} automatically unfold the modal definitions and thus can be used with modal connectives and quantifiers as they are used with the usual connectives and quantifiers. Nothing else needs to be done. For the modal operators, however, the following simple tactics have been implemented, in order to allow the user to work with the concepts of \emph{necessity} and \emph{possibility} without having to unfold the definitions of modal operators and think in terms of possible worlds. These tactics remind rules of labelled calculi for modal logics.

@@

\noindent
Validity of a modal proposition is validity of its grounding on any world.

@@

\noindent
The following lemmas are convenient

@@

Note: possible worlds machinery is hidden from the user.
